Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-24 paper_comparison/paper_comparison/paper_comparison.tex

\caption{Power of different tests on lineups with different fitted value distributions. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline within its group. Conventional tests are more sensitive than visual tests in regards of the type of the visual pattern and the fitted value distribution. Visual tests exhibit relatively low power in testing non-linearity patterns under discrete uniform distribution, possibly due to the difficulty in reading discreteness. Meanwhile, uneveness affects heteroskedasticity patterns greatly, result in low power of visual tests under normal and lognormal distribution.}\label{fig:different-x-dist-poly-power}
\end{figure}

@@

\caption{Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. }\label{fig:poly-power-j}
\end{figure}

@@

>>>>

\caption{Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power.}\label{fig:different-x-dist-poly-power}
\end{figure}

@@

\caption{Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. Power curves with higher order of non-linearity are drawn with deeper colours.}\label{fig:poly-power-j}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  summarise paper content
\item
  briefly describe what was learned
\item
  how does this apply more broadly than simple regression
\item
  where does this lead? Computer vision residual plot reading
\end{enumerate}

\hypertarget{acknowledgement}{%
\section{Acknowledgement}\label{acknowledgement}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  software tools
\item
  point to github repo (create a new one)
\item
  summarise the supplementary material
\end{enumerate}
